Arc Blanc: a real time ocean simulation framework

### 2024-11-14 paper.tex
Fix Donelan-Banner Hulk normalization factor explanation

Note that we applied a first normalization factor $Q_{DB}$ to the simple Donelan Banner spectrum (Equation \ref{equa:ddb}) before calculating this second normalization factor $\widetilde{Q_{DB\xi}}(r_{\omega})$. In fact, if we simply approximate the full-spectrum normalization factor before applying it, we will be faced with a normalization problem, because for small values of $r_{\omega}$, $Q_{DB\xi}(\omega)$ will be very low and therefore numerically difficult to normalize.

>>>>

Note that a first normalization factor $Q_{DB}$ is applied to the Donelan-Banner spectrum (Equation \ref{equa:ddb}) before calculating the second normalization factor $\widetilde{Q_{DB\xi}}(r_{\omega})$. In fact, a normalization problem will occur if the full-spectrum normalization factor is simply approximated before its application, because for small values of $r_{\omega}$, $Q_{DB\xi}(\omega)$ will be very low and therefore numerically challenging to normalize.
